%----------------------------------------------------------------------------------------
%	DOCUMENT DEFINITION
%----------------------------------------------------------------------------------------

\documentclass[a4paper,8pt]{extarticle}  % 7pt to fit one page

%----------------------------------------------------------------------------------------
%	FONT
%----------------------------------------------------------------------------------------

\usepackage{helvet}
\renewcommand{\familydefault}{\sfdefault}

%----------------------------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------------------------
\usepackage{url}
\usepackage{parskip}
\setlength{\parskip}{0pt}

\usepackage{color}
\usepackage{graphicx}
\usepackage[usenames,dvipsnames]{xcolor}
\usepackage[margin=0.5in]{geometry}

\usepackage{tabularx}
\usepackage{enumitem}
\setlist{nosep,leftmargin=1em,itemsep=2pt}
\newcolumntype{C}{>{\centering\arraybackslash}X}

\usepackage{titlesec}
\usepackage{multicol}
\usepackage{multirow}
\titleformat{\section}{\large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{4pt}{4pt}

\usepackage[unicode, draft=false]{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour,linkcolor=linkcolour}

\usepackage{fontawesome5}

%----------------------------------------------------------------------------------------
%	BEGIN DOCUMENT
%----------------------------------------------------------------------------------------
\begin{document}
\pagestyle{empty}

%----------------------------------------------------------------------------------------
%	TITLE
%----------------------------------------------------------------------------------------
\begin{tabularx}{\linewidth}{@{} C @{}}
\Huge{\textbf{Neeraj Butola}} \\[5.5pt]
\href{https://github.com/Frostdev7506}{\raisebox{-0.02\height}\faGithub\ GitHub} $|$
\href{https://www.linkedin.com/in/neeraj-butola/?originalSubdomain=in}{\raisebox{-0.02\height}\faLinkedin\ LinkedIn} $|$
\href{https://neerajbutola.netlify.app}{\raisebox{-0.02\height}\faGlobe\ Portfolio} $|$
\href{mailto:Neerajbutola8910@gmail.com}{\raisebox{-0.02\height}\faEnvelope\ Neerajbutola8910@gmail.com} $|$
\href{tel:+918779341486}{\raisebox{-0.05\height}\faMobile\ +91-8779341486} \\
\end{tabularx}

%----------------------------------------------------------------------------------------
% PROFESSIONAL SUMMARY
%----------------------------------------------------------------------------------------
\section{Professional Summary}
\textbf{Senior Full Stack (MERN) + Cloud Engineer} with 3.7+ years building secure, scalable products across \textbf{MongoDB, Express.js, React/React Native, Node.js} and \textbf{Python} backends. Spearheaded end-to-end delivery of microservice platforms on \textbf{AWS} (EC2, ECS/EKS, S3, CloudFront, Lambda), implemented \textbf{Nginx reverse proxy}, rate limiting, security headers, API key auth, and robust CI/CD. Frontend specialist in \textbf{React, Next.js, Vite} with \textbf{pixel-perfect} UI and strong \textbf{SEO} (CWV, structured data). Deep experience with \textbf{Strapi}, \textbf{Redis}, \textbf{Kafka}, \textbf{NATS}, \textbf{Kubernetes}, and event-driven architectures. 

%----------------------------------------------------------------------------------------
% WORK EXPERIENCE
%----------------------------------------------------------------------------------------
\section{Work Experience}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Software Engineer (Neoveda Technologies)} & \hfill Jul 2025 -- Present \\[3pt]
\multicolumn{2}{@{}X@{}}{
\begin{minipage}[t]{\linewidth}
\begin{itemize}
  \item[--] \textbf{Spearheaded migration} of Node.js microservices powering an AI workflow product (\emph{similar to Boltic-class orchestration}) to a \textbf{containerized architecture} on \textbf{Kubernetes (EKS)} with \textbf{event-driven} patterns using \textbf{Kafka} and \textbf{NATS}; improved deployment velocity and reliability.
  \item[--] Led \textbf{service decomposition \& decoupling} from monolithic services into domain-aligned microservices; standardized \textbf{API contracts}, observability, retries, and backoff policies across \textbf{Node.js/Express} services.
  \item[--] Developed and maintained \textbf{full-stack applications} with \textbf{React} and \textbf{Angular} frontends consuming backend REST APIs; implemented component-based UI design and state management for high performance.
  \item[--] \textbf{Architected RESTful APIs} from scratch — including route design, async flow, authentication, and validation; applied best practices for idempotency, pagination, and caching. Ensured adherence to REST principles and security measures (rate limiting, JWT/OAuth2).
  
  \item[--] Designed resilient systems with \textbf{Node.js clusters}, streams, buffers, and inter-process communication (spawn/fork/patch); optimized memory handling and implemented tools to fix potential memory leaks.
  \item[--] Built and optimized SQL procedures and indexes across \textbf{PostgreSQL}, \textbf{MySQL}, and \textbf{MongoDB}; wrote stored procedures, analyzed query plans, and tuned indexes for high-volume transactions.
  \item[--] Developed \textbf{secure ingress with Nginx}, enforced API key validation, HSTS, CSP, CORS, and rate limits; integrated \textbf{Redis} for caching and queueing; optimized \textbf{raw SQL} execution paths for hot transactions.
  \item[--] Owned \textbf{SEO \& performance metrics}: Next.js SSR/ISR, Core Web Vitals (LCP/CLS/INP), sitemaps, canonical/OG tags, schema.org; CDN tuning on \textbf{CloudFront}.
  \item[--] Integrated \textbf{Strapi CMS} for headless content management; developed webhook-driven pipelines connecting CMS events with backend microservices.
  
\end{itemize}
\end{minipage}
}
\end{tabularx}


\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{Associate Software Developer (ONEAGROW FINTECH)} & \hfill May 2023 -- Jul 2025 \\[3pt]
\multicolumn{2}{@{}X@{}}{
\begin{minipage}[t]{\linewidth}
\begin{itemize}
  \item[--] \textbf{Owned end-to-end architecture \& delivery} for \textbf{Greattr} fintech suite: React/React Native frontends, Node/Express microservices, and data stores (PostgreSQL/MSSQL/MongoDB).
  \item[--] \textbf{Built from scratch on AWS}: frontend on \textbf{S3 + CloudFront}; backend on \textbf{EC2} and \textbf{ECS} for decoupled services; blue/green deploys with Docker and GitHub Actions.
  \item[--] \textbf{Integrated 3rd-party platforms} at scale: \emph{KYC/eKYC (Aadhaar/OKYC), payments, SMS/email, analytics, maps, notifications (FCM/SES/SNS)}, and fraud signals; standardized adapters and secrets management.
  \item[--] Implemented \textbf{Nginx reverse proxy} as edge gateway (TLS, API key checks, rate limiting, security headers, strict CORS); hardened Linux hosts.
  \item[--] Delivered \textbf{pixel-perfect} UIs with \textbf{React, Next.js, Vite, React Native}; design-system governance, a11y, and performance budgets.
  \item[--] \textbf{Performance \& reliability}: hot paths via \textbf{raw SQL} (no ORM), lazy loading caching with redis and usage of async queues(Bull/BullMQ), idempotency keys, and saga-style workflows to ensure at lest Eventual consistency.
\end{itemize}
\end{minipage}
}
\end{tabularx}

\begin{tabularx}{\linewidth}{ @{}l r@{} }
\textbf{New Associate (Accenture)} & \hfill Dec 2021 -- Apr 2023 \\[3pt]
\multicolumn{2}{@{}X@{}}{
\begin{minipage}[t]{\linewidth}
\begin{itemize}
  \item[--] Supported enterprise apps on \textbf{Azure/AWS} using \textbf{React, Node.js, Express, MongoDB}; automated CI/CD with GitHub Actions, Docker, Bash/Python.
  \item[--] Built reusable React components (Hooks/Redux) and improved reliability with Redis caching and CDN integration.
\end{itemize}
\end{minipage}
}
\end{tabularx}

%----------------------------------------------------------------------------------------
% PROJECTS
%----------------------------------------------------------------------------------------
\section{Projects}

\begin{tabularx}{\linewidth}{@{}l r@{}}
\textbf{Pupils - Student LMS (PostgreSQL, Node, Express, React, Tailwind, Redux)} & \hfill \href{https://github.com/Frostdev7506/PupilSyncServer}{View Demo} \\[3pt]
\multicolumn{2}{@{}X@{}}{
\begin{minipage}[t]{\linewidth}
\begin{itemize}
  \item[--] Role-based auth, REST APIs, and secure deployments on Linux; \textbf{React + Vite + Tailwind} for responsive, accessible UI.
  \item[--] AWS SNS for real-time notifications; modular services with clean interfaces for future mobile integrations.
\end{itemize}
\end{minipage}
}
\end{tabularx}

\begin{tabularx}{\linewidth}{@{}l r@{}}
\textbf{Greattr - Fintech Apps (React Native, React, Node, Express, MSSQL, PostgreSQL)} & \hfill \href{https://github.com/Frostdev7506/Lyriks}{View Demo} \\[3pt]
\multicolumn{2}{@{}X@{}}{
\begin{minipage}[t]{\linewidth}
\begin{itemize}
  \item[--] \textbf{Greenfield build on AWS}: frontend via \textbf{S3 + CloudFront}; backend on \textbf{EC2 + ECS}; pipelines with Docker \& GitHub Actions; Linux hardening.
  \item[--] \textbf{Pixel-perfect} web \& mobile UI using \textbf{React, Next.js, Vite, React Native}; consistent design tokens and theming.
  \item[--] Security-first: Nginx gateway with \textbf{API key} auth, TLS, CSP, HSTS, \textbf{rate limiting}, strict CORS; \textbf{sanitized inputs} and SQL hardening.
  \item[--] Data \& messaging: Redis caching/queues, \textbf{Kafka/NATS} for events; hot paths with optimized \textbf{raw SQL} (no ORM).
  \item[--] Rich integrations: \textbf{KYC}, payments, \textbf{FCM}, email/SMS, analytics, maps; dashboards for real-time merchant insights.
\end{itemize}
\end{minipage}
}
\end{tabularx}

\begin{tabularx}{\linewidth}{@{}l r@{}}
\textbf{Greattr Onboarding Portal (PostgreSQL, Node, Cypress, Python, Angular)} & \hfill \href{https://www.greattr.com}{View Demo} \\[3pt]
\multicolumn{2}{@{}X@{}}{
\begin{minipage}[t]{\linewidth}
\begin{itemize}
  \item[--] Scalable onboarding with Angular + Node; \textbf{OKYC Aadhaar} for eKYC and e-sign; Cypress suites and Dockerized CI/CD.
\end{itemize}
\end{minipage}
}
\end{tabularx}

%----------------------------------------------------------------------------------------
% EDUCATION
%----------------------------------------------------------------------------------------
\section{Education}
\begin{tabularx}{\linewidth}{@{}l X@{}}
2017 -- 2020 & \textbf{Bachelor of Science in Computer Science}, Mumbai University \\
\end{tabularx}

%----------------------------------------------------------------------------------------
% CERTIFICATIONS
%----------------------------------------------------------------------------------------
\section{Certifications}
\begin{tabularx}{\linewidth}{@{}l X l@{}}
\textbf{AWS Certified Cloud Practitioner} & & \textbf{Microsoft Certified: Azure Administrator (AZ-104)} \\
\textbf{Azure Fundamentals (AZ-900)} & & \textbf{Azure Security (SC-900)} \\
\textbf{Azure Data Fundamentals (DP-900)} & & \textbf{Azure AI Fundamentals (AI-900)} \\
\end{tabularx}

%----------------------------------------------------------------------------------------
% TECHNICAL SKILLS
%----------------------------------------------------------------------------------------
\section{Technical Skills}
\begin{tabularx}{\linewidth}{@{}l X@{}}
\textbf{Frontend:} & \textbf{React}, React Native, Next.js, Vite, Tailwind, Redux, TypeScript, Accessibility (WCAG), SEO (CWV, schema.org) \\
\textbf{Backend:} & \textbf{Node.js}, Express.js, Python (Flask/FastAPI), REST APIs, Microservices, \textbf{Strapi (Headless CMS)} \\
\textbf{Data/Messaging:} & \textbf{MongoDB}, PostgreSQL, MySQL, MSSQL, \textbf{Redis}, \textbf{Kafka}, \textbf{NATS} \\
\textbf{Cloud/DevOps:} & \textbf{AWS (EC2, S3, CloudFront, ECS, EKS, Lambda)}, Docker, Kubernetes, Nginx, CI/CD (GitHub Actions), CloudWatch \\
\textbf{Security:} & API Keys, TLS/HTTPS, CORS, CSP/HSTS, Rate Limiting, Input Sanitization, SQL Hardening, Linux Hardening \\
\end{tabularx}

\vfill
\end{document}

